% !TeX spellcheck = en_US

\chapter{Acknowledgments}

First of all, I would like to express my deepest gratitude to my supervisor and mentor Gabi Schaumann for her unparalleled support ever since I walked through her office door for my first student research project back in 2012. I have always greatly appreciated your extraordinary and inspiring way of thinking, our frank exchange of views, and that you keep pushing me to go the extra mile. Thank you for always believing in me and letting me work so independently on my projects, including this very one.
My sincere thanks extends to Katherine Muñoz and Geert Cornelis for co-supervising me and giving such valuable and encouraging feedback on my work.

I am further indebted to Silvia Eichhöfer for her constant help and practical advise in the laboratory that far exceeded that of an ``ordinary'' technician. This similarly applies to Angelika Holderle, our working group secretary, who keeps things running.

Thank you also to my former bachelor and master students Julius Albert, Orasai Faikhaw, Aaron Kintzi, Sven Korz, Paul Löffler, Nguyen Minh Trang, Simon Rudolph, and Heike Schröder who beared my supervision, kept rethinking my ideas, and challenged me to explain complex matters in a simple way. I really enjoyed working with you and still do with those who became my colleagues afterwards.
Special thanks goes to my office mates, Christian Buchmann, Kilian Kenngott, and Maximilian Meyer, who are not just acknowledged for their great help and support but above all for being such good friends. Thank you to the entire Group of Environmental and Soil Chemistry, most notably Dörte Diehl, Jan David, and Mathilde Knott, for the inspiring and friendly work atmosphere.

Further, I would like to thank Mirka Viitala and Yuri Park for hosting me during my way too short research stay at LUT, Finland, as well as our guest researchers Giselle Anahi Berenstein from UNGS, Argentina, and Wiebke Mareile Heinze from SLU, Sweden, for advancing the field together. Thank you also to Berit Schütze, Daniela Thomas, and Elke Brandes at \foreignlanguage{ngerman}{Thünen Institut} for our fruitful cooperation. I am looking forward to the projects to come!

I would also like to thank Michaela Maier, Manfred Schmitt, and Robert Gaschler from the Faculty of Psychology for their comments and feedback on the sociocultural and psychological implications of plastic mulching. Josef Hejl (PETKA CZ, Czech Republic), Michael Schöneich (Netzsch, Germany), and Tanja Butt (Retsch, Germany) are acknowledged for helping with our first \acs{tga-ms} experiments. Thank you also to Sabine Mann (S-prep, Germany) and Karen Sam (CDS Analytical, US) for their kind assistance with our pyrolyzer. It really did an awesome job during the last years. Moreover, thanks to Peter Gebler and Wendy Höpp for English editing. Without you, this thesis would definitely be harder to read.

\vspace{\baselineskip}

\foreignlanguage{ngerman}{Schließlich möchte ich meiner Familie, meinen Freunden und vor allem meiner Freundin Sarah für ihr Verständnis, ihre Geduld und Unterstützung während der letzten Jahre danken. Ohne euch hätte diese Arbeit bei doppelter Anstrengung wohl nur halb so viel Spaß gemacht. Danke, dass es euch gibt!}
