% !TeX spellcheck = en_US

\chapter{Screening for Plastic Debris in Agricultural Soil Covered with Plastic Films}
\label{ch:screening}

\paragraph{Abstract} Agricultural plastic covers\marginnote{This chapter was adapted from: \fullcite{SteinmetzAre2021}.\par See Page~\pageref{ch:author-contributions} for \nameref{ch:author-contributions}.} made from \ac{pe} and \ac{pp} provide increased yields and an improved crop quality. However, such covers are suspected of partially breaking down into smaller debris and thereby contributing to soil pollution with microplastics. To scrutinize this, we randomly sampled 240 topsoil cores (\SIrange{0}{5}{\centi\meter}) from eight fields which were covered with fleeces, perforated foils, and plastic mulches for less than two years. Samples from the field periphery (\SI{50}{\meter} perimeter) served as a reference. Visual plastic debris \SI{>2}{\milli\meter} was analyzed by \ac{ftir}--\ac{atr}. Smaller, soil-associated plastic debris was dispersed from \SI{50}{\gram} of fine soil (\SI{<=2}{\milli\meter}) using sodium hexametaphosphate solution and density-separated with saturated \ch{NaCl} solution. The collected \ac{pe}, \ac{pp}, and \ac{ps} debris was selectively dissolved in a mixture of \ac{tcb} and \textit{p}-xylene at \SI{150}{\degreeCelsius} and quantified by \ac{py-gc-ms}. We counted six \ac{pe} and \ac{ps} fragments \SI{>2}{\milli\meter} in two out of eight fields. By contrast, Py-GC/MS analysis revealed \ac{pe}, \ac{pp}, and \ac{ps} contents \SI{>1}{\micro\gram\per\gram} in seven fields (\SI{17}{\percent} of all samples). In three fields, \ac{pe} levels of \SIrange{3}{35}{\micro\gram\per\gram} were associated with the use of thinner and less durable perforated foils (\SI{40}{\micro\meter} thickness). This was slightly more pronounced at field edges where the plastic covers are turned and weighted down. By contrast, \SI{50}{\micro\meter} thick \ac{pe} films were not shown to emit any plastic debris. \Ac{pp} contents of \SIrange{5}{10}{\micro\gram\per\gram} were restricted to single observations in the field centers of three sites. On one site, we found expanded \ac{ps} particles \SI{>2}{\milli\meter} that concurred with elevated \ac{ps} levels (\SIrange{8}{19}{\micro\gram\per\gram}) in the fine soil. Both \ac{pp} and \ac{ps} were distributed indistinctly across sites so that their source remained unresolved. In addition, the extent to which plastic contents of up to \SI{7}{\micro\gram\per\gram} in the field periphery of some sites were attributed to wind drift from the covered fields or from external sources needs to be investigated in future studies. Yet, our results suggest that the short-term use of thicker and more durable plastic covers should be preferred to limit plastic emissions and accumulation in soil.

\section{Introduction}